Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-09-02 paper/main.tex
filled in w/ standing figures + sections

% bare_jrnl_compsoc, texV1.4b, 2015/08/26, Michael Shell

\documentclass[10pt,journal,compsoc]{IEEEtran}

@@

% *** CITATION PACKAGES ***
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

@@

% *** MATH PACKAGES ***
\usepackage{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
\usepackage{algorithmic}

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
% IEEEtran contains the IEEEeqnarray family of commands

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
\title{Topological Equivariant Artist Model for Visualization Library Architecture}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.
%~\IEEEmembership{Member,~IEEE,}
\author{Hannah~Aizenman, Thomas~Caswell, and~Michael~Grossberg,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem H. Aizenman and M. Grossberg are with the department of Computer Science, City College of New York. 
\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: haizenman@ccny.cuny.edu, mgrossberg@ccny.cuny.edu 
\IEEEcompsocthanksitem Thomas Caswell is with National Synchrotron Light Source II, Brookhaven National Lab 
\protect \\
E-mail: tcaswell@bnl.gov}% <-this % stops an unwanted space
\thanks{Manuscript received X XX, XXXX; revised X XX, XXXX.}
}

@@

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
% Computer Society journal (but not conference!) papers do something unusual
% with the very first section heading (almost always called "Introduction").
% They place it ABOVE the main text! IEEEtran.cls does not automatically do
% this for you, but you can achieve this effect with the provided
% \IEEEraisesectionheading{} command. Note the need to keep any \label that
% is to refer to the section immediately after \section in the above as
% \IEEEraisesectionheading puts \section within a raised box.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015
\section{Introduction}
\section{Related Work}
\subsection{Continuity}
\subsection{Equivariance}
\subsection{Category Theory}
\section{Topological Equivariant Artist Model}
- brief intro to artist in most simple form $\A\rightarrow H$

\subsection{Data Bundle}
\subsubsection{Continuity: Base Space K}
\subsection{Equivariance: Fiber F}
\subsection{Structured Data: Section \tau}
\subsubsection{Continuity of Data: sheaf $\mathscr{O}$}
\subsection{Graphic Bundle} %probably doesn't all need to be subsections, just figure + short description
\subsubsection{Continuity: Base Space H}
\subsubsection{Equivariance: Fiber D}
\subsubsection{Structured Data: Graphic \rho}
\subsection{Artist}
%% flesh out categorical framing of artist, walk through how eq 16 is part of implementing the artists
%% https://github.com/story645/proposal/blob/main/notes/meetings/2021_08_30.md

\subsubsection{Continuity: xi}
% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol
\subsubsection{Visual Bundle: V}
\subsubsection{Visual encodings: nu} %look at what K&S call these stages
\subsubsection{Visual composition: Q} % look at what K&S call these stages
\subsection{Combining Artists}
\section{Case Study}
\section{Discussion}
\subsection{Limitations}
\subsection{future work}

@@

\appendices
\section{Rendering: Rho}
\section{Manufacturing Q: Q_hat}

@@

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Hannah Aizenman}
Biography text here.
\end{IEEEbiographynophoto

>>>>

% bare_jrnl_compsoc, texV1.4b, 2015/08/26, Michael Shell
\documentclass[10pt,journal,compsoc]{IEEEtran}

@@

\usepackage[nocompress]{cite}

@@

% *** MATH PACKAGES ***
\usepackage{amsmath}
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath,amsfonts,amssymb,eulervm,xspace}
%\usepackage{mathrsfs} % math script fonts

% *** SPECIALIZED LIST PACKAGES ***
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{subfig} %ieee does not like subfigure
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?
\usepackage[switch]{lineno}
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   framesep=3mm} 
% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{tabulary}
% IEEEtran contains the IEEEeqnarray family of commands

@@

\usepackage{notation} %notation conventions
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
\title{Topological Equivariant Artist Model for Visualization Library Architecture}
% author names and IEEE memberships
\author{Hannah~Aizenman, Thomas~Caswell, and~Michael~Grossberg,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem H. Aizenman and M. Grossberg are with the department of Computer Science, City College of New York. 
\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: haizenman@ccny.cuny.edu, mgrossberg@ccny.cuny.edu 
\IEEEcompsocthanksitem Thomas Caswell is with National Synchrotron Light Source II, Brookhaven National Lab 
\protect \\
E-mail: tcaswell@bnl.gov}% <-this % stops an unwanted space
\thanks{Manuscript received X XX, XXXX; revised X XX, XXXX.}
}

@@

\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.
\section{Related Work}
\subsection{Continuity}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{k_different_types.png}
\end{figure}
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
\subsection{Equivariance}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{equiv.png}
\end{figure}

\subsection{Category Theory}

\section{Topological Equivariant Artist Model}
%%- brief intro to artist in most simple form $\A\rightarrow H$

\subsection{Data Bundle \dtotal}
\begin{figure}[!t]

\end{figure}
\paragraph{Continuity: Base Space \dbase}
\paragraph{Equivariance: Fiber \dfiber}
\paragraph{Structured Data: Section \dsection}
\subsubsection{Continuity of Data: sheaf $\mathcal{O}$}
\begin{figure}
  \includegraphics[width=2.5in]{sheaf.png}
  \caption{Maybe create a figure that shows what the sheaf does, like 
  https://www.euclideanspace.com/maths/topology/sheaf/index.htm}
\end{figure}
\subsection{Visual Bundle \gtotal} %probably doesn't all need to be subsections, just figure + short description
\begin{figure}
  \includegraphics[width=2.5in]{render.png}
\end{figure}
\paragraph{Continuity: Base Space \gbase}
\paragraph{Equivariance: Fiber \gfiber}
\paragraph{Structured Data: Visual \gsection}
\subsection{Artist}
%% flesh out categorical framing of artist, walk through how eq 16 is part of implementing the artists
%% https://github.com/story645/proposal/blob/main/notes/meetings/2021_08_30.md

\subsubsection{Visual to Data: \vindex}
\begin{figure}[!t]
  \includegraphics[width=2.5in]{xi.png}
\end{figure}
\subsubsection{Representation Bundle: \vtotal}

\subsubsection{Data to Representation: \vchannel} %look at what K&S call these stages
\begin{figure}[!t]
  \includegraphics[width=2.5in]{nu.png}
\end{figure}

\subsubsection{Representation to Visual: \vmark} % look at what K&S call these stages
\begin{figure}[!t]
  \includegraphics[width=2.5in]{q.png}
\end{figure}

\begin{figure}[!t]
  \includegraphics[width=2.5in]{path_of_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

\subsection{Combining Artists}
\begin{figure}[!t]
\centering
\subfloat[Artists with shared $\mu_i$ renderered correctly]{\includegraphics[width=2.5in]{combined_artist.png}%
\label{fig_first_case}}
\hfil
\subfloat[Artists without shared $\mu_i$]{\includegraphics[width=2.5in]{exploding_artist.png}%
\label{fig_second_case}}
\caption{Simulation results for the network.}
\label{fig_sim}
\end{figure}

\section{Case Study}

\section{Discussion}
\subsection{Limitations}
\subsection{future work}

@@

\appendices
\section{Rendering: \gsection}
\section{Manufacturing $\vmarkd \leftarrow \vmark$}

@@

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Hannah Aizenman}
Biography text here.
\end{IEEEbiographynophoto}
